%\title{My two column CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by
% the template found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%
\documentclass{tccv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\begin{document}

\part{Alex Rocha}

\section{Work Experience}

\begin{eventlist}

\item{December 2015 -- Current}
    {Ilegra, Porto Alegre}
    {Full Stack Developer}

    Developer companies in government projects made in Scala and Java.

\item{December 2014 -- December 2015}
    {Eldorado Research Institute, Porto Alegre}
    {Software Engineering}

    Developer on projects for a multinational in mobile telephone area using various technologies including python , java and agile methods.

\item{August 2013 -- December 2014}
    {Datacom, Eldorado do Sul}
    {JAVA Developer}

    Developer of the network management software DmView.
    Software developed in Java for both web and desktop plataforms using, Swing, JSF, Spring Framework and Apache JBoss/Wildfly.
    Continuous Integration with jenkins. Version Control using Git. Code Review process using
    Gerrit.

\item{January 2012 - August 2013}
    {Associação Zen Budista do Rio Grande do Sul, Via Zen}
    {JAVA Developer}

    Developer of Via Zen home page and CMS for content management. Using JSF, JPA, RichFaces, Facelets and MySQL.

\item{March 2011 -- December 2013}
    {BlueDot, Soluções em Tecnologia}
    {Co-founder}

    Co-founder of Bluedot, a software development company specialized in enterprise solutions.

\item{September 2009 -- October 2009}
    {FAURGS}
    {JAVA Developer}

    Third-party developer for SICREDI\@. Worked with Seam Framework, Hibernate, JSF technologies and Oracle
    database.

\item{August 2007 -- July 2013}
    {Institudo dos Advogados do Rio Grande do Sul, IARGS}
    {JAVA/PHP Developer}

    Software architect and developer of ERP for IARGS\@.
    Financial control software developed in Java, with a desktop and a web module.

\end{eventlist}

\personal
[alexrochas.github.io]
{Rua Fonseca Ramos, 168\newline 90870-300 -- Porto Alegre (RS)}
{(51) 8539-1843 }
{alex.rochas@yahoo.com.br}

\section{Education}

\begin{yearlist}

\item{2012 -- 2015}
    {Analysis and System Development}
    {Uniritter, Porto Alegre}

\end{yearlist}

\section{Languages}

\begin{factlist}
\item{English}{Intermediate}
\item{French}{Basic}
\item{Japanese}{Basic}
\end{factlist}

\section{Skills}

\begin{factlist}

\item{Advanced}
    {JAVA, Linux, HTML, CSS}

\item{Intermediate}
    {Git, Ruby, PHP, Windows, MySQL, Postgresql, Javascript, {\LaTeX}}

\item{Basic}
    {Python, Scala, C, Oracle, Shell Script}

\end{factlist}

\section{Other}

\begin{factlist}

\item{\href{https://github.com/alexrochas}{GitHub}}
    {https://github.com/alexrochas}

\item{\href{http://www.linkedin.com/pub/alex-rocha/72/35/92}{Linkedin}}
    {http://www.linkedin.com/pub/\linebreak[1]alex-rocha/72/35/92}

\item{\href{https://www.facebook.com/alex.rocha.88}{Facebook}}
{https://www.facebook.com/\linebreak[1]alex.rocha.88}

\end{factlist}

\end{document}
